Supplementary Information: Vulnerability of tree growth

### 2025-01-27 doc/supplementary_information.Rmd
supplementary information update

---
title: "Supplementary Information: Vulnerability of tree growth"
author: 
date: 
output: 
  pdf_document:
    fig_caption: yes
    toc: true # table of content true
    toc_depth: 2  
bibliography: growth-precip-thailand.bib
suppress-bibliography: false
csl: methods-in-ecology-and-evolution.csl
header-includes:  \usepackage{float}
                  \usepackage{caption}
                  \captionsetup[table]{font=footnotesize}
                  \captionsetup[figure]{font=footnotesize}
                  \captionsetup[figure]{labelformat=empty}
                  \captionsetup[table]{labelformat=empty}
                  \usepackage{pdflscape}
                  \newcommand{\blandscape}{\begin{landscape}}
                  \newcommand{\elandscape}{\end{landscape}}
---

@@

#Appendices

#SI table numbers

#SI table captions

#SI figure numbers

#SI figure captions

#https://github.com/EcoClimLab/Operations/blob/master/Data_Management-Scientific_Workflow/manuscript_prep_with_Rmd.md
```

```{r read files, echo=F}
# Read in files

```
\newpage

>>>>

---
title: "Supplementary Information: Vulnerability of tree growth"
author: 
date: 
output: 
  pdf_document:
    fig_caption: yes
    toc: true # table of content true
    toc_depth: 2  
bibliography: growth-precip-thailand.bib
suppress-bibliography: false
csl: new-phytologist.csl
header-includes:  \usepackage{float}
                  \usepackage{caption}
                  \captionsetup[table]{font=footnotesize}
                  \captionsetup[figure]{font=footnotesize}
                  \captionsetup[figure]{labelformat=empty}
                  \captionsetup[table]{labelformat=empty}
                  \usepackage{pdflscape}
                  \newcommand{\blandscape}{\begin{landscape}}
                  \newcommand{\elandscape}{\end{landscape}}
---

@@

# Appendices

# SI table numbers

# SI table captions

# SI figure numbers

# SI figure captions

# https://github.com/EcoClimLab/Operations/blob/master/Data_Management-Scientific_Workflow/manuscript_prep_with_Rmd.md
```

```{r read files, echo=F}
# Read in files
```

\newpage

## Climate data and correlations

![](../results/plots/climate_data_timeseries_2007_2019.png)

![](../results/plots/climate_data_correlations.png)

\newpage

## Data cleaning additional methods

\newpage

## Species traits and correlations

\newpage

## Individual model diagnostics

\newpage
